\documentclass{article}
\usepackage{mathtools}
\usepackage{setspace}
\usepackage{textcomp}
\pagenumbering{gobble}
\pagestyle{myheadings}
\markright{ Resume David Evans \hfill \today}
\usepackage[margin=0.34in]{geometry}
%\setlength{\topmargin}{-.5in}
%\setlength{\textheight}{9in}
%\setlength{\oddsidemargin}{.110in}
%\setlength{\textwidth}{7in}
\begin{document}
\begin{centering}   
\Huge{David Evans} \\
\large{  1128 Spaight Street, Madison, WI 53703 \\
651-528-0375 $|$ evans.dave.michael@gmail.com} \\ 
\bigskip

%\parbox[t][3.6cm][t]{0.9\textwidth}{I am a recent graduate with a passion for working with soils, especially with quantifying and explaining soil variability. I am proficient at describing and sampling soils in the field and am adept with spatial and non-spatial statistics as well as GIS analysis. I have given numerous presentations of my work and am published in a major scientific journal. My goal is to be involved with projects where I work with and study soils in order to better understand their use and management. %With my good attitude and strong work ethic, I am a great addition to any team. In addition to my abilities with analyses and fieldwork, I am an excellent communicator and team--member.

%Whether collecting data from the field or analyzing data in the office. I soils. I am interested inMy master's project taghtwork digital soil mapping 
%I have worked on projects where it was necessary to compile and organize data on a regional scale and on projects where the analyses were conducted on a field scale. 
\onehalfspacing
\end{centering}
\noindent \large{EDUCATION}\\
\line(1,0){580}\\ \normalsize
\textbf{University of Wisconsin-Madison}\\
Master of Science, Soil Science; GPA: 3.719 \hfill August 2013\\
\indent Concentration: spatial analysis and pedology\\
\noindent Bachelor of Science, Soil Science; GPA: 3.714 \hfill May 2011\\
\indent Concentration: field crop production\\

\noindent \large{SKILL SET}\\ 
%\begin{small}
\line(1,0){580}
%I've got to find some way to get skills and software somewhat separated
%\end{small}
%\noindent 

\parbox[t][3cm][t]{0.4\textwidth}{\textbullet Statistical analysis and inference\\
\textbullet GIS theory and practice\\
\textbullet Web Development\\
%\textbullet Spatial statistics, including kriging, point pattern analysis, and regression\\
% \textbullet Field description of soils\\
% \textbullet Laboratory analysis and procedures\\
\textbullet Communication of results and methods in written and oral forms} 
\parbox[t][2.5cm][t]{0.07\textwidth}{\hfil}
\parbox[t][3.2cm][t]{0.45\textwidth}{Techniques and software proficiencies:\\
\small{
	\textbullet Django Framework\\
	\textbullet VB.NET\\	
	\textbullet R and Python programming languages\\
	\textbullet ArcGIS, QGIS, and SAGA-GIS\\
	\textbullet Git version control software\\
	\textbullet SWAT and ArcSWAT watershed modeling software\\
	% \textbullet Python 
	\textbullet GDAL/OGR spatial data libraries\\
% \textbullet GPS equipment and methodologies\\
% \textbullet Classification according to US Soil Taxonomy
% \textbullet The typesetting software \LaTeX\\
}}
%\fbox{\parbox[t][4em][c]{0.33\textwidth}{Some \\ text} }


\noindent \large{RELEVANT EXPERIENCE}\\ \begin{small}
% % % %
\line(1,0){580}\\
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\noindent \textbf{IS Data Services -- Department of Natural Resources} \hfill \textbf{July 2014 -- Present}
\begin{itemize}
\item Assemble and organize spatial and non-spatial data for large watershed modeling project.
\item Carryout statistical analysis for the regionalization of hydrologic model parameters. 
\item Assist with the development of a spatial analysis tool 
 for predicting erosion and improving water quality.
\end{itemize}
% ----------------------------------------------------------- %
\noindent \textbf{Assistant GIS Technician -- Natural Resources Conservation Service} \hfill \textbf{January 2014 -- June 2014}
\begin{itemize}
\item Assist in the maintenance of wetland determinations database.
\item Conduct orthorectification and wetland map creation. 
\end{itemize}
% ----------------------------------------------------------- %
\noindent \textbf{GIS Analyst -- UW-Madison Soil Science, Nutrient Cycling and Agroecosystems Lab} \hfill \textbf{October 2013 -- June 2014}
\begin{itemize}
\item Facilitate the investigation of fine-scale soil variation in a fertilizer management study.
\item Conduct spatial analysis of interaction of nitrogen rate and soil property in relation to crop yield.
%\item Carry out statistcal anaysis to determine where and how fertilizer can be applied most profitably.
\end{itemize}
% ----------------------------------------------------------- %
\noindent \textbf{Project Coordinator -- UW-Madison Soil Science, F.D. Hole Soils Lab} \hfill \textbf{August 2013 -- June 2014}
\begin{itemize}
\item Coordinate the progress and maintenance of map display and development for Wisconsin branch of the ISEE Project.
\item Develop maps of landscapes and soil properties for educational purposes.
\item Organize and maintain database of geospatial information.
%\item Create workflow for map creation and revision.
%\item Investigate workflow for managing revisions and updates to published maps.
\end{itemize}
% ----------------------------------------------------------- %
\noindent \textbf{Research Assistant -- UW-Madison Soil Science, F.D. Hole Soils Lab} \hfill \textbf{Sept 2011 -- June 2013}
\begin{itemize}
\item Used digital soil mapping techniques to produce quantitative maps of soil properties.
\item Described and classified soils in the field according to US Soil Taxonomy.
\item Investigated soil-landscape relationships through statistical and conceptual models.
\end{itemize}
% -------------------- %
%\noindent \textbf{Field Assistant -- UW-Madison Soil Science, Nutrient Cycling and Agroecosystems Lab} \hfill \textbf{March 2010 -- Aug 2011}
%\begin{itemize}
%\item Managed analysis of soil and water samples; compiled data for multi-site, multi-year study.
%\item Prepared and maintained research plots with field technicians.
%\item Collected, catalogued, and processed soil, water, biomass, and grain samples.
%\end{itemize}
% -------------------- %
\noindent \textbf{Investigator -- UW-Madison Soil Science, Bioretention Pond Permeability Project} \hfill \textbf{Fall 2010 -- Spring 2011}
\begin{itemize}
\item Investigated causes for the failure of a stormwater retention basin with a team of professors, graduate and undergraduate students.
\item Conducted laboratory analysis to test hypotheses regarding the soil properties contributing to basin failure.
\item Communicated potential solutions to hydrologists and urban planners.\\
\end{itemize}
% -------------------- %
%\noindent \textbf{Participant -- NACTA Soil Judging Contest} \hfill \textbf{Spring 2011}
%\begin{itemize}
%\item Silver medal in individual category of national soil judging competition against fifty students from nine colleges and universities.
%\item Identification, description, and classification of soils in the field.
%\item As captain, led team members in weekly meetings and practices.\\
%\end{itemize}
% -------------------- %
\end{small}

\noindent \large{SELECTED PRESENTATIONS \& PUBLICATIONS}\\ 
% % % %
\line(1,0){580}\\

%\noindent \line(1,0){580}
\begin{small}
\leftskip 0.1in
\parindent -0.1in
% % % % % % % % % % % % % % % % % % % %
Ruesch, A. S., A. Mynsberge, and D. M. Evans. ``Introduction to Python in ArcGIS.'' 18 February, 2015. A workshop given at the Wisconsin Land Information Association in Green Bay, WI.\\

% % % % % % % % % % % % % % % % % % % %
%EVANS, D.M. & A.E. HARTEMINK 2014 Digital soil mapping of a red clay subsoil covered by loess. Geoderma (in the press)
Evans, D. M. and A. E. Hartemink. ``Digital soil mapping of a red clay subsoil covered by loess.'' 2014. Geoderma 230-231, 296-304.\\
% % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % %
%Evans, D. M. and A. E. Hartemink. ``Digital Soil Mapping of Terra Rossa in Southern Wisconsin.'' 22 October, 2012. Presentation given at the New %Challenges for Digital Soil Mapping: I, session at the ASA, CSSA and SSSA Annual Meetings in Cincinnati, OH.\\
% % % % % % % % % % % % % % % % % % % %
%Evans, D. M. and A. E. Hartemink. ``Mapping the Presence of Red Clay Subsoil in the Driftless Area of
%Wisconsin, USA.'' \textit{Digital Soil Assessments and Beyond: Proceedings of the 5th Global Workshop on Digital Soil Mapping 2012}, Sydney, Australia. Minasny, B., Malone, B. P., and McBratney, A. B. CRC Press. July, 2012.\\
% % % % % % % % % % % % % % % % % % % %

Evans, D. M., K. Rudersdorf, G. Obear, S. Griffith, M.R. Naber, and P. Barak. ``Saline and Sodic Soils in Wisconsin: The Sad Story of the Costco Infiltration Pond.'' 12 September, 2012. Presentation given to USGS Water Resources Meeting, Madison, WI.\\


\end{small}

\end{document}
